API design for machine learning software: experiences from the scikit-learn project

### 2013-06-24 paper.tex
Institutions.
Not that bad...

\author{Lars~Buitinck~\inst{1,2} \and
        Gilles~Louppe~\inst{1,2} \and
        Mathieu~Blondel~\inst{1,2} \and
        Fabian~Pedregosa~\inst{2} \and
        Andreas~Mueller~\inst{2} \and
        Olivier~Grisel~\inst{2} \and
        Vlad~Niculae~\inst{2} \and
        Peter~Prettenhofer~\inst{2} \and
        Alexandre~Gramfort~\inst{2} \and
        Jacques~Grobler~\inst{2} \and
        Robert~Layton~\inst{2} \and
        Jake~Vanderplas~\inst{2} \and
        Arnaud~Joly~\inst{2} \and
        Brian Holt~\inst{2} \and
        Gaël~Varoquaux~\inst{2}}

\institute{Main authors of the present paper \and
           Core contributors to the project}

@@

Lars Buitinck is a ... Gilles Louppe is a research fellow of the Fonds de la
Recherche Scientifique-FNRS (Belgium) and acknowledges its financial support.
Mathieu Blondel is a ...

>>>>

\author{Lars~Buitinck~\inst{1} \and
        Gilles~Louppe~\inst{2} \and
        Mathieu~Blondel~\inst{3} \and
        Fabian~Pedregosa~\inst{4} \and
        Andreas~Mueller~\inst{5} \and
        Olivier~Grisel~\inst{6} \and
        Vlad~Niculae~\inst{7} \and
        Peter~Prettenhofer~\inst{8} \and
        Alexandre~Gramfort~\inst{9} \and
        Jacques~Grobler~\inst{4} \and
        Robert~Layton~\inst{10} \and
        Jake~Vanderplas~\inst{11} \and
        Arnaud~Joly~\inst{2} \and
        Brian Holt~\inst{12} \and
        Gaël~Varoquaux~\inst{4}}

\institute{University of Amsterdam \and
           University of Liège \and
           Kobe University \and
           Parietal, INRIA Saclay \and
           University of Bonn \and
           Nuxeo \and 
           University of Bucharest \and
           Bauhaus-Universitat \and
           Telecom ParisTech \and
           University of Ballarat \and
           University of Washington \and
           Samsung Electronics Research Institute}

@@
